### 2013-06-06 inst/examples/BUGS/process-noise-only.Rmd
whoops, didn't take log of mu

  "
  iQ <- 1 / (stdQ * stdQ);
  r0 <- exp(logr0)
  theta <- exp(logtheta)
  y[1] ~ dunif(0, 10)
  for(t in 1:(N-1)){
    mu[t] <- y[t] * exp(r0 * (1 - y[t]/K)* (y[t] - theta) / K )
    y[t+1] ~ dlnorm(mu[t], iQ) 
  }
}")
writeLines(bugs.model, "allen_process.bugs")
```

@@

  "
  iQ <- 1 / (stdQ * stdQ);
  r0 <- exp(logr0)
  y[1] ~ dunif(0, 10)
  for(t in 1:(N-1)){
    mu[t] <- y[t] * exp(r0 * (1 - y[t]/K) )
    y[t+1] ~ dlnorm(mu[t], iQ) 
  }
}")
writeLines(bugs.model, "ricker_process.bugs")
```

@@

  y[1] ~ dunif(0, 10)
  for(t in 1:(N-1)){
    mu[t] <- r0 * pow(abs(y[t]), theta) / (1 + pow(abs(y[t]), theta) / K)
    y[t+1] ~ dlnorm(mu[t], iQ) 
  }
}")
writeLines(bugs.model, "myers_process.bugs")
```

>>>>

  "
  iQ <- 1 / (stdQ * stdQ);
  r0 <- exp(logr0)
  theta <- exp(logtheta)
  y[1] ~ dunif(0, 10)
  for(t in 1:(N-1)){
    mu[t] <- log(y[t]) + r0 * (1 - y[t]/K)* (y[t] - theta) / K 
    y[t+1] ~ dlnorm(mu[t], iQ) 
  }
}")
writeLines(bugs.model, "allen_process.bugs")
```

@@

  "
  iQ <- 1 / (stdQ * stdQ);
  r0 <- exp(logr0)
  y[1] ~ dunif(0, 10)
  for(t in 1:(N-1)){
    mu[t] <- log(y[t]) + r0 * (1 - y[t]/K) 
    y[t+1] ~ dlnorm(mu[t], iQ) 
  }
}")
writeLines(bugs.model, "ricker_process.bugs")
```

@@

  y[1] ~ dunif(0, 10)
  for(t in 1:(N-1)){
    mu[t] <- log(r0)  + theta * abs(y[t]) - log(1 + pow(abs(y[t]), theta) / K)
    y[t+1] ~ dlnorm(mu[t], iQ) 
  }
}")
writeLines(bugs.model, "myers_process.bugs")
```
